---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```


# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....



# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

We are interested in the height of Lake Huron (@fig-huronheight)

```{r}
#| label: fig-huronheight
#| fig-cap: Annual measurements of the height, in feet, of Lake Huron 1875-1972
#| echo: false

tibble(year = 1875:1972,
       level = as.numeric(datasets::LakeHuron)) |>
  ggplot(aes(x = year, y = level)) +
  labs(x = "Year", 
       y = "Height (ft)") +
  geom_point() +
  theme_bw()
```

We are interested in the height of 31 black cherry trees (@fig-blackcherrytrees)
```{r}
#| label: fig-blackcherrytrees
#| fig-cap: Height of 31 Black Cherry Trees
#| echo: false

datasets::trees |> 
  as_tibble() |> 
  ggplot(aes(y = Height)) +
  geom_bar() +
  labs(x = "Number of Black Cherry Trees", y = "Height (ft)") + 
  theme_bw()

```
We are interested in the weight of chicks in grams, by how old they were (@fig-chicks)

```{r}

#| label: chicks
#| fig-cap: Weight versus age of chicks
#| echo: false


datasets::ChickWeight |> 
  as_tibble() |> 
  ggplot(aes(x = Time, y = weight, group = Chick)) +
  geom_line() +
  labs(x = "Age (days)", y = "Weight (gm)") +
  theme_minimal()

```


We are interested in the number of sunspots from 1700 to 1988 (@fig-sunspots)

```{r}
#| label: fig-sunspots
#| fig-cap: Number of sunspots from 1700 to 1988
#| echo: false

tibble(year = 1700:1988,
       sunspots = as.numeric(datasets::sunspot.year) |> round(0)) |>
  ggplot(aes(x = sunspots)) +
  labs(x= "Number of sunspots", y = "Year") +
  geom_histogram()

```



```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it. 


We are interested in penguins and their silly business (@fig-penguins)

```{r}
#| label: fig-penguins
#| fig-cap: Ugly graph


ggplot(data = penguins,
       aes(x = flipper_length_mm,
           y = body_mass_g)) +
  geom_point(aes(color = species, shape = sex),
             size = 20,
             alpha = .7) +
  scale_color_manual(values = c("red", "pink", "red")) +
  labs(
    title = "Penguins are mean, ur mom's house",
    subtitle = "Toe length and mass for ADeLIe, ChINSTRAP and gEnToo peNGuiNS",
    x = "Flipper length (houses)",
    y = "Body mass (bluberries)",
    color = "Penguin species"
  ) +
  theme_minimal() +
  theme(
    legend.position = c(0.7, 0.9),
    plot.title.position = "plot",
    title = element_text(size=24, face='bold'),
    plot.caption = element_text(hjust = 0, face = "italic"),
    plot.caption.position = "plot"
  )

```



# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.  

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.


### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.


# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```




# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows... 

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```



\newpage


# References


